Geneus: An Enigma of Organism Intelligence

### 2019-12-17 paper/paper.tex
Add data figure.

This is the data. \cite{Authors14}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{data.png}
  \caption{Visualization of the data-processing pipeline.}
  \label{fig:data}
\end{figure}

A flowchart of the data collection and processing pipeline can be seen in Figure \ref{fig:data}. The process involves collecting data from Wikipedia and then processing it into representations that will be used as inputs for the deep learning model.

\subsection{Scrape index pages}
The first step is to creates lists of species articles which is done by supplying manually-found species index pages using \texttt{species\_url\_scraper.py} which then scrapes these articles to output lists of Wikipedia article URLs.

\subsection{Scrape species articles} The next step consumes these lists and scrapes the Wikipedia pages themselves to extract the scientific classification as well as the text content from each of the sections.
